The Impact of Uncertainty on Monetary Transmission

### 2023-10-17 US/draft.Rmd
Updates: Endogeneity

\textcolor{red}{WRITE SOMETHING ABOUT THE RESULTS HERE 1-2 PARAGRAPHS.}

@@

```
```{=latex}
\caption{Interest rates \label{fig:interest}}
\end{figure}
```

In an alternative specifications the FFR is replaced with the 1-Year Treasury Yield. While the two show high co-movement, the latter may carry some additional information such as market expectations or yield curve dynamics, that might have an impact on the results.

@@

```{=latex}
\caption{Economic Policy Uncertainty index \label{fig:epu}}
\bigskip
\footnotesize
\textit{Notes}: The blue and red lines indicate the median and 70th percentile of the historical distribution respectively.
\end{figure}
```

In @baker2016measuring, along with the main EPU index, several EPU Categorical indices are also constructed. These indices are more specific to a certain topic within "economic" or "economic policy" such as monetary policy, fiscal policy, or sovereign debt crises. In order to pinpoint the source of uncertainty that might be most influential for the transmission of monetary policy shocks, I repeat the estimations with the EPU Categorical indices in place of the main EPU index. The EPU categorical indices can be seen in Figure \ref{fig:epucat} of the Appendix.

It is important to mention that there are a number of alternative^[These measures can be seen in Figure \ref{fig:unces} of the Appendix.] measurements of uncertainty in the literature. These indices are for example the Equity Market-related Economic Uncertainty Index of @baker2016measuring; the Geopolitical Risk Index and the Trade Policy Uncertainty Index of @caldara2022measuring and @caldara2020economic; the World Uncertainty Index of @ahir2022world; as well as the VIX Index and the TED spread. In this paper, only the EPU and its Categorical indices are considered as measures of uncertainty.

@@

To address some potential issues, a number of robustness checks are conducted. Firstly, I replace the FFR in $Y_ {t}$ with the 1-Year Treasury Yield and the FFR shadow rate. Secondly, I check if the results hold if I change the construction of the regime indicator from $X_{t}$ to $X_{t-1}$, making it pre-determined, and thereby eliminating the potential of estimating the impact of two contemporaneous shocks. Thirdly, I incorporate the uncertainty index in its levels as well as a financial stress indicator in order to void their effects from the aggregates during the estimation^[Please refer to the [Alternative model specifications] of the Appendix for further details on how Equation \ref{eq:1} above changes].

@@

irfs %>% 
  select(-mult, -restr) %>% 
  filter(label != 'R') %>% 
  filter(spec == 'main',
         control == 'none',
         index == 'epu') %>% 
  ggplot(aes(x = t, y = median, color = thresh, fill = thresh,
             ymin = lower, ymax = upper
  )) +
  geom_line(linewidth = lw) +
  geom_hline(yintercept = 0, color = "red") +
  geom_ribbon(alpha=.1, linetype=0) + 
  facet_wrap(regime~label, scales = "free")+
  theme_minimal() +
  theme(plot.title = element_text(size = 11, hjust=0.5),
        axis.title.y = element_text(size=11),
        legend.position = 'none') +
  scale_color_manual(breaks = c('0.5', '0.7'),
                     values = c('#0074D9', '#FF4136')) +
  scale_fill_manual(breaks = c('0.5', '0.7'),
                    values = c('#0074D9', '#FF4136')) +
  labs(x = "",
       y ="")

@@

```{=latex}
\caption{Regime specific impulse responses, original specification. \label{fig:epumedirfs}}
\bigskip
\footnotesize
\textit{Notes}: The blue solid line represents the posterior median obtaied with the threshold value $\mu$ set to the median, the red one with it set to the 70th percentile of the EPU. The shaded areas represent the 84\% confidence bands calculated from the posterior impulse response draws.
\end{figure}
```

There are some noteworthy differences from these results compared to previous literature. As discussed in the Literature section of this paper, @aastveit2017economic and @aquino2022does show that the transmission efficacy is eroded by high economic uncertainty, while @horvathTBAuncertain find a considerably more prolonged period of contraction induced by monetary shocks in high uncertainty.

Results from this estimate suggest that the contemporaneous drop in output is slightly larger in low uncertainty, with the following quarters showing a similar level of contraction. Alongside this, disinflation caused by the monetary shock is significantly enhanced in the high uncertainty regime compared to the low uncertainty one.

Comparing the median and the 70th percentile as threshold levels for the regime switches, the responses of inflation in the lower regime and of output in the higher regime are not too dissimilar, however their opposite uncertainty regime counterparts show some key differences. Firstly, the output contraction in the low regime is elevated when switching to the higher uncertainty threshold. This is in line with the findings of @horvathTBAuncertain, as allocating a larger proportion of observations previously labelled as high uncertainty would support the notion of larger contraction of high uncertainty times. Secondly, we can observe that the response of inflation shifts upwards as we increase the threshold level - albeit retaining a similar shape. This lies closer to the findings of @aastveit2017economic and @aquino2022does as the implication from this suggest that more extreme levels of uncertainty would erode the transmission.

\textcolor{red}{EZT AMÚGY MAJD MÁSHOVA RAKNÁM.}^[To further clarify, global uncertainty measures are likely better at capturing one of the mechanisms, through which geoeconomic fragmentation impacts economies, as noted in @ilyna2023geo. While here and and in the cited previous literature, country-specific uncertainty measures carry a different implication, whereby policy uncertainty explicitly reduces the efficacy of the transmission of policy actions.]

@@

Through conducting a number of robustness tests, controlling for the level of uncertainty, using a more traditional TVAR model where the indicator is constructed from $t-1$ values of the threshold variable, or using 1-Year rates instead of the FFR has no significant impact on the results. However, controlling for the Zero-Lower-Bound, as well as financial stress both change the results significantly.

```{=latex}
\begin{figure}[!htbp]
```
```{r}
irfs %>% 
  select(-mult, -restr) %>% 
  filter(label != 'R') %>% 
  filter(spec == 'shadow',
         control == 'financial_stress',
         index == 'epu',
         thresh == '0.7') %>% 
  ggplot(aes(x = t, y = median)) +
  geom_line(linewidth = lw) +
  geom_hline(yintercept = 0, color = "red") +
  facet_wrap(regime~label, scales = "free")+
  theme_minimal() +
  theme(plot.title = element_text(size = 11, hjust=0.5),
        axis.title.y = element_text(size=11),
        legend.position = 'none') +
  labs(x = "",
       y ="")
```
```{=latex}
\caption{Regime specific impulse responses, updated specification. \label{fig:epumedirfs}}
\bigskip
\footnotesize
\textit{Notes}: Interest rates are measured by the Shadow Rate, the threshold value is set to the 70th percentile of the EPU index.
\end{figure}
```

@@

First, the "narrative" of the uncertainty index could matter. In @baker2016measuring, additional to the EPU index, several categorical indices are constructed^[Please refer to Figure \ref{fig:epucat}.]. Replicating the simulations with each categorical index could provide insight into how such narratives can impact the transmission mechanism. Notably, uncertainty specifically related to monetary policy should be the most insightful. Below in Figure \ref{fig:narrative}

```{=latex}
\begin{figure}[!htbp]
```
```{r narrative, fig.height=10}
irfs %>% 
  select(-mult, -restr) %>% 
  filter(label != 'R',
         spec == 'shadow',
         index != 'epu',
         control == 'financial_stress') %>% 
  group_by(label, regime, spec, control, thresh, index) %>% 
  mutate(median = purrr::accumulate(.x = median, 
                                    .f = sum,
                                    .dir = 'forward'),
         upper = purrr::accumulate(.x = upper, 
                                    .f = sum,
                                    .dir = 'forward'),
         lower = purrr::accumulate(.x = lower, 
                                    .f = sum,
                                    .dir = 'forward')) %>% 
  filter(t == max(t)) %>% 
  select(-t, -upper, -lower) %>% 
  spread(label, median) %>% 
  mutate(sac = Y/PI,
         regime = str_remove_all(regime, ' uncertainty'),
         thresh = case_when(thresh == '0.5' ~ 'Median',
                            thresh == '0.7' ~ '70th Perc.'),
         thresh = factor(thresh, levels = c('Median', '70th Perc.')),
         index = case_when(index == 'epu' ~ 'EPU',
                           index == 'epu_debt' ~ 'EPU: Debt, crises',
                           index == 'epu_finreg' ~ 'EPU: Fin. Regulation',
                           index == 'epu_fis' ~ 'EPU: Fiscal Policy',
                           index == 'epu_mon' ~ 'EPU: Monetary Policy',
                           index == 'epu_reg' ~ 'EPU: Regulation',
                           index == 'epu_trade' ~ 'EPU: Trade Policy')) %>% 
  ggplot(aes(x = regime, y = sac, fill = regime)) + 
  geom_col( color = 'black', width = 0.3, position = position_dodge(width = 0.1)) +
  facet_grid(index~thresh, scales = 'free') +
  theme_minimal()+
  theme(legend.position = 'none') +
  labs(x = '',
       y = '') + 
  scale_fill_manual(breaks = c('High',
                                'Low'),
                     values = c('#8B0000',
                                '#00008B'))

```
```{=latex}
\caption{Sacrifice ratios. \label{fig:narrative}}
\bigskip
\footnotesize
\textit{Notes}: The sacrifice ratios are calculated from the accumulated impact of the policy shocks over the 20 quarter horizon.  
\end{figure}
```

@@

```{=latex}
\caption{EPU Categorical uncertainty indices \label{fig:epucat}} 
\bigskip
\footnotesize
\textit{Notes}: The blue and red lines indicate the median and 70th percentile of the historical distribution respectively.
\end{figure}
```

```{=latex}
\begin{figure}[!htbp]
```
```{r otherunc}

@@

```{=latex}
\caption{Additional uncertainty measures \label{fig:unces}}
\bigskip
\footnotesize
\textit{Notes}: The blue and red lines indicate the median and 70th percentile of the historical distribution respectively.
\end{figure}
```

## Alternative model specifications

@@

\begin{equation} \label{eq:2}
  Y_{t} = \sum\limits_{k=1}^{4}\Theta_{high}I(X_{t} \ge \mu)Y_{t-k} + \sum\limits_{k=1}^{4}\Theta_{low}I(X_{t} < \mu)Y_{t-k} + \sum\limits_{k=1}^{4}\beta X_{t-k} + \epsilon_{t}
\end{equation}

\begin{equation} \label{eq:3}
  Y_{t} = \sum\limits_{k=1}^{4}\Theta_{high}I(X_{t} \ge \mu)Y_{t-k} + \sum\limits_{k=1}^{4}\Theta_{low}I(X_{t} < \mu)Y_{t-k} + \sum\limits_{k=1}^{4}\gamma Z_{t-k} + \epsilon_{t}
\end{equation}

@@

```
```{=latex}
\caption{Influence of uncertainty \label{fig:contemp}}
\bigskip
\footnotesize
\textit{Notes}: The black line shows the base specification, the green, red and blue lines show results obtained with one-quarter lag uncertainty-based regime indicator, uncertainty added as a control variable, and the combination of these two specifications respectively.
\end{figure}
```

As discussed in the Data section of this paper, there are alternative interest rate measures to calculate policy shocks from. Using the 1-Year Treasury Yield over the Federal Funds Rate has the benefit of - to some extent - carrying information about future expectations. The other alternative is the @wu2016measuring Shadow Rate, the added benefit of which is the additional information about implied rates of interest in times when the former two were close to the Zero-Lower-Bound. The data for the Shadow Rate is available in a shorter time span from `r min(drop_na(select(data2[['macro_alt']], date, ffr_shadow))$date) %>% quarterly_format()` to `r max(drop_na(select(data2[['macro_alt']], date, ffr_shadow))$date) %>% quarterly_format()`, however the exclusion of data from before the 1990s as well as 2022 should not cause concerns.

@@

```
```{=latex}
\caption{Policy impact calculated with different rates \label{fig:shockmes}}
\bigskip
\footnotesize
\end{figure}
```

As seen in Figure \ref{fig:shockmes}, the difference between responses obtained when the policy shock is calculated using the FFR and the 1-Year Treasury Yield show little difference, however accounting for implied rates via the Shadow Rate has considerable impact on the results. With the threshold level set to the median, both regimes responses shift downwards, and with the 70th percentile, this is only seen in high uncertainty responses. Such results do support the finding of shocks in high uncertainty times having a larger contractionary effect due to uncertainty causing an increase in volatility.

@@

```
```{=latex}
\caption{Financial stress versus no controls \label{fig:finstress}}
\bigskip
\footnotesize
\textit{Notes}: In both the No Controls and the Fin. Stress estimations, the Shadow Rate is used to estimate policy shocks.
\end{figure}
```

>>>>

Results from a TVAR model estimated with a full set of controls indicates that 
\textcolor{red}{WRITE SOMETHING ABOUT THE RESULTS HERE 1-2 PARAGRAPHS.}

@@

```{=latex}
\caption{Interest rates \label{fig:interest}}
\end{figure}
```
In an alternative specifications the FFR is replaced with the 1-Year Treasury Yield. While the two show high co-movement, the latter may carry some additional information such as market expectations or yield curve dynamics, that might have an impact on the results.

@@

```{=latex}
\caption{Economic Policy Uncertainty index \label{fig:epu}}
\bigskip
\footnotesize
\textit{Notes}: The blue and red lines indicate the median and 70th percentile of the historical distribution respectively.
\end{figure}
```
In @baker2016measuring, along with the main EPU index, several EPU Categorical indices are also constructed. These indices are more specific to a certain topic within "economic" or "economic policy" such as monetary policy, fiscal policy, or sovereign debt crises. In order to pinpoint the source of uncertainty that might be most influential for the transmission of monetary policy shocks, I repeat the estimations with the EPU Categorical indices in place of the main EPU index. The EPU categorical indices can be seen in Figure \ref{fig:epucat} of the Appendix.

It is important to mention that there are a number of alternative[^4] measurements of uncertainty in the literature. These indices are for example the Equity Market-related Economic Uncertainty Index of @baker2016measuring; the Geopolitical Risk Index and the Trade Policy Uncertainty Index of @caldara2022measuring and @caldara2020economic; the World Uncertainty Index of @ahir2022world; as well as the VIX Index and the TED spread. In this paper, only the EPU and its Categorical indices are considered as measures of uncertainty.

[^4]: These measures can be seen in Figure \ref{fig:unces} of the Appendix.

@@

To address some potential issues, a number of robustness checks are conducted. Firstly, I replace the FFR in $Y_ {t}$ with the 1-Year Treasury Yield and the FFR shadow rate. Secondly, I check if the results hold if I change the construction of the regime indicator from $X_{t}$ to $X_{t-1}$, making it pre-determined, and thereby eliminating the potential of estimating the impact of two contemporaneous shocks. Thirdly, I incorporate the uncertainty index in its levels as well as a financial stress indicator in order to void their effects from the aggregates during the estimation[^5].

[^5]: Please refer to the [Alternative model specifications] of the Appendix for further details on how Equation \ref{eq:1} above changes

@@

irfs %>% 
  select(-mult, -restr) %>% 
  filter(label != 'R') %>% 
  filter(spec == 'main',
         control == 'none',
         index == 'epu') %>% 
  ggplot(aes(x = t, y = median, color = thresh, fill = thresh,
             ymin = lower, ymax = upper
  )) +
  geom_line(linewidth = lw) +
  geom_hline(yintercept = 0, color = "red") +
  geom_ribbon(alpha=.2, linetype=0) + 
  facet_wrap(regime~label, scales = "free")+
  theme_minimal() +
  theme(plot.title = element_text(size = 11, hjust=0.5),
        axis.title.y = element_text(size=11),
        legend.position = 'none') +
  scale_color_manual(breaks = c('0.5', '0.7'),
                     values = c('#0074D9', '#FF4136')) +
  scale_fill_manual(breaks = c('0.5', '0.7'),
                    values = c('#0074D9', '#FF4136')) +
  labs(x = "",
       y ="")

@@

```{=latex}
\caption{Regime specific impulse responses, original specification. \label{fig:epumedirfs}}
\bigskip
\footnotesize
\textit{Notes}: The blue solid line represents the posterior median obtaied with the threshold value $\mu$ set to the median, the red one with it set to the 70th percentile of the EPU. The shaded areas represent the 84\% confidence bands calculated from the posterior impulse response draws.
\end{figure}
```
There are some noteworthy differences from these results compared to previous literature. As discussed in the Literature section of this paper, @aastveit2017economic and @aquino2022does show that the transmission efficacy is eroded by high economic uncertainty, while @horvathTBAuncertain find a considerably more prolonged period of contraction induced by monetary shocks in high uncertainty.

Results from this estimate suggest that the contemporaneous drop in output is slightly larger in low uncertainty, with the following quarters showing a similar level of contraction. Alongside this, disinflation caused by the monetary shock is significantly enhanced in the high uncertainty regime compared to the low uncertainty one. Comparing the median and the 70th percentile as threshold levels for the regime switches, the responses of inflation in the lower regime and of output in the higher regime are not too dissimilar, however their opposite uncertainty regime counterparts show some key differences.

Firstly, the output contraction in the low regime is elevated when switching to the higher uncertainty threshold. This is in line with the findings of @horvathTBAuncertain, as allocating a larger proportion of observations previously labelled as high uncertainty would support the notion of larger contraction of high uncertainty times. Secondly, we can observe that the response of inflation shifts upwards as we increase the threshold level - albeit retaining a similar shape. This lies closer to the findings of @aastveit2017economic and @aquino2022does as the implication from this suggest that more extreme levels of uncertainty would erode the transmission.

Why might these results differ so drastically from previous works? Firstly, in @horvathTBAuncertain globally aggregated uncertainty measures are used. As noted in @ilyna2023geo, heightened uncertainty is a channels of geoeconomic fragmentation, and uncertainty measured on the global level is likely a better proxy of this, thereby having somewhat different implications. Additionally, @aastveit2017economic and @aquino2022does use a wider range of variables, which can help isolate how uncertainty interacts with the transmission mechanism.

Studying the relationship between policy shocks and (policy) uncertainty naturally raises the question of whether or not the uncertainty index is endogenous to policy innovations. Investigating the potential endogeneity can also guide in selecting the appropriate model specification. Testing for endogeneity is done by running Granger causality tests between the EPU index and the posterior median of the residuals obtained from alternative specifications considered. The results from a select number of these is shown here in Table \ref{tab:grang}^[The Linear model is added as a point of comparison for the TVAR models. It is estimated on the FFR, CPI inflation rate and GDP growth rate without further control variables. Full control TVAR represents models estimated with lagged values of the EPU index and the St. Louis FED Financial Stress Indicator added as controls.].

```{=latex}
\begin{center}
`r xtable::xtable(read_rds('data/granger.rds'), type = "latex", digits = 3, align = c("p{0.1cm}", "p{9cm}", "p{2cm}", "p{2cm}"),label = 'tab:grang', caption = 'Granger causality tests with alternative model specifications',
display = c('g', 'g', 'g', 'g'))`
\end{center}
```

The results of these tests suggests that in most cases we fail to reject the null, and thus policy shocks do not drive uncertainty, neither the other way around. Interpreting the p-values as the likelihood of $H0$ to be true, there are a handful of conclusions to draw. The likelihood of policy shocks driving uncertainty stay reasonably high irrespective of specification, however, for the reverse causality case, it varies substantially. Firstly, the likelihood of uncertainty being a driver of policy shocks considerably increases when switching from the median to the 70th percentile threshold. This is likely due to the low number of observations in the regime. Secondly, using the Shadow rate^[Why the Shadow rate might be a more desirable measure is further discussed in the Robustness checks of the Appendix.] over the FFR also considerably reduces this likelihood. Given these, the superior specification should be a TVAR with a full set of controls estimated with the threshold level set to the median. The next subsection showcases the impulse responses estimated from this.

@@

Through conducting a number of robustness^[Discussed in further detail in the Appendix.] and endogeneity tests, we arrive at a model that should grasp best how uncertainty influences the transmission of policy shocks. Figure \ref{fig:updatedirfs} below shows the impulse responses obtained with the new specification after controlling for the level of uncertainty and financial stress.

```{=latex}
\begin{figure}[!htbp]
```
```{r}
irfs %>% 
  select(-mult, -restr) %>% 
  filter(label != 'R') %>% 
  filter(spec == 'main',
         control == 'both',
         index == 'epu',
         thresh == '0.5') %>% 
  ggplot(aes(x = t, y = median, ymin = lower, ymax = upper)) +
  geom_line(linewidth = lw) +
  geom_hline(yintercept = 0, color = "red") +
  geom_ribbon(alpha = .2)+
  facet_wrap(regime~label, scales = "free")+
  theme_minimal() +
  theme(plot.title = element_text(size = 11, hjust=0.5),
        axis.title.y = element_text(size=11),
        legend.position = 'none') +
  labs(x = "",
       y ="")
```

```{=latex}
\caption{Regime specific impulse responses, updated specification. \label{fig:updatedirfs}}
\bigskip
\footnotesize
\textit{Notes}: In the updated specification, interest rates are measured by the FFR, the threshold value is set to the median of the EPU index, lagged values of the EPU and the St. Louis FED Financial Stress Indicator are added as controls.
\end{figure}
```

These results indicate that some of the findings from both @aastveit2017economic, @aquino2022does and @horvathTBAuncertain can be true at the same time. In high uncertainty times, the impact of the monetary shock is considerably elevated on impact, and the first few quarters after the shock. However, dissipates much more rapidly from the variables, even reverting from disinflation to inflation around 12-16 quarters after the shock. The larger impact around the time of the shock supports the idea, that inflates the variance of expectations, and thereby increasing the impact of shocks.

On the other hand, in times of low uncertainty, the impact is comparatively smaller, however the persistence of the impulse responses is greater, leading to the the adjustment of prices and output being slower, staying below 0 over the 20 quarter horizon. This indicates lower variance and more stability in the expectations of agents in the economy.

@@

In @baker2016measuring, additional to the EPU index, several categorical indices are constructed[^Please refer to Figure \ref{fig:epucat}.]. To investigate how the underlying cause behind uncertainty interacts with the transmission mechanism, I replicate the estimation with each of these categorical indices. For easier comparability, I calculate sacrifice ratios - foregone output as a fraction of deterred inflation - from the 20-quarter accumulated impulse responses.

Replicating the simulations with each categorical index could provide insight into how such narratives can impact the transmission mechanism. Notably, uncertainty specifically related to monetary policy should be the most insightful. The sacrifice ratios can be seen in Figure \ref{fig:narrative} below.

```{=latex}
\begin{figure}[!htbp]
```
```{r narrative, fig.height=10}
irfs %>% 
  select(-mult, -restr) %>% 
  filter(label != 'R',
         spec == 'main',
         index != 'epu',
         control == 'both') %>% 
  group_by(label, regime, spec, control, thresh, index) %>% 
  mutate(median = purrr::accumulate(.x = median, 
                                    .f = sum,
                                    .dir = 'forward'),
         upper = purrr::accumulate(.x = upper, 
                                    .f = sum,
                                    .dir = 'forward'),
         lower = purrr::accumulate(.x = lower, 
                                    .f = sum,
                                    .dir = 'forward')) %>% 
  filter(t == max(t)) %>% 
  select(-t, -upper, -lower) %>% 
  spread(label, median) %>% 
  mutate(sac = Y/PI,
         regime = str_remove_all(regime, ' uncertainty'),
         thresh = case_when(thresh == '0.5' ~ 'Median',
                            thresh == '0.7' ~ '70th Perc.'),
         thresh = factor(thresh, levels = c('Median', '70th Perc.')),
         index = case_when(index == 'epu' ~ 'EPU',
                           index == 'epu_debt' ~ 'EPU: Debt, crises',
                           index == 'epu_finreg' ~ 'EPU: Fin. Regulation',
                           index == 'epu_fis' ~ 'EPU: Fiscal Policy',
                           index == 'epu_mon' ~ 'EPU: Monetary Policy',
                           index == 'epu_reg' ~ 'EPU: Regulation',
                           index == 'epu_trade' ~ 'EPU: Trade Policy')) %>% 
  ggplot(aes(x = regime, y = sac, fill = regime)) + 
  geom_col( color = 'black', width = 0.3, position = position_dodge(width = 0.1)) +
  facet_grid(index~thresh, scales = 'free') +
  theme_minimal()+
  theme(legend.position = 'none') +
  labs(x = '',
       y = '') + 
  scale_fill_manual(breaks = c('High',
                                'Low'),
                     values = c('#8B0000',
                                '#00008B'))

```{=latex}
\caption{Sacrifice ratios. \label{fig:narrative}}
\bigskip
\footnotesize
\textit{Notes}: The Full control TVAR model is used for estimating the data behind the sacrifice ratios.  
\end{figure}
```

\textcolor{red}{CALCULATE OVER DIFFERENT HORIZONS INSTEAD OF THE TWO MU-s YOU DUMMY! SHORT TERM GAINS OVER LONG TERM LOSSES}

@@

```{=latex}
\caption{EPU Categorical uncertainty indices \label{fig:epucat}} 
\bigskip
\footnotesize
\textit{Notes}: The blue and red lines indicate the median and 70th percentile of the historical distribution respectively.
\end{figure}
```
```{=latex}
\begin{figure}[!htbp]
```
```{r otherunc}

@@

```{=latex}
\caption{Additional uncertainty measures \label{fig:unces}}
\bigskip
\footnotesize
\textit{Notes}: The blue and red lines indicate the median and 70th percentile of the historical distribution respectively.
\end{figure}
```
## Alternative model specifications

@@

```{=tex}
\begin{equation} \label{eq:2}
  Y_{t} = \sum\limits_{k=1}^{4}\Theta_{high}I(X_{t} \ge \mu)Y_{t-k} + \sum\limits_{k=1}^{4}\Theta_{low}I(X_{t} < \mu)Y_{t-k} + \sum\limits_{k=1}^{4}\beta X_{t-k} + \epsilon_{t}
\end{equation}
```
```{=tex}
\begin{equation} \label{eq:3}
  Y_{t} = \sum\limits_{k=1}^{4}\Theta_{high}I(X_{t} \ge \mu)Y_{t-k} + \sum\limits_{k=1}^{4}\Theta_{low}I(X_{t} < \mu)Y_{t-k} + \sum\limits_{k=1}^{4}\gamma Z_{t-k} + \epsilon_{t}
\end{equation}
```
```{=tex}
\begin{equation} \label{eq:4}
  Y_{t} = \sum\limits_{k=1}^{4}\Theta_{high}I(X_{t} \ge \mu)Y_{t-k} + \sum\limits_{k=1}^{4}\Theta_{low}I(X_{t} < \mu)Y_{t-k} + + \sum\limits_{k=1}^{4}\beta X_{t-k} + \sum\limits_{k=1}^{4}\gamma Z_{t-k} + \epsilon_{t}
\end{equation}
```

@@

```{=latex}
\caption{Influence of uncertainty \label{fig:contemp}}
\bigskip
\footnotesize
\textit{Notes}: The black line shows the base specification, the green, red and blue lines show results obtained with one-quarter lag uncertainty-based regime indicator, uncertainty added as a control variable, and the combination of these two specifications respectively.
\end{figure}
```
As discussed in the Data section of this paper, there are alternative interest rate measures to calculate policy shocks from. Using the 1-Year Treasury Yield over the Federal Funds Rate has the benefit of - to some extent - carrying information about future expectations. The other alternative is the @wu2016measuring Shadow Rate, the added benefit of which is the additional information about implied rates of interest in times when the former two were close to the Zero-Lower-Bound. The data for the Shadow Rate is available in a shorter time span from `r min(drop_na(select(data2[['macro_alt']], date, ffr_shadow))$date) %>% quarterly_format()` to `r max(drop_na(select(data2[['macro_alt']], date, ffr_shadow))$date) %>% quarterly_format()`, however the exclusion of data from before the 1990s as well as 2022 should not cause concerns.

@@

```{=latex}
\caption{Policy impact calculated with different rates \label{fig:shockmes}}
\bigskip
\footnotesize
\end{figure}
```
As seen in Figure \ref{fig:shockmes}, the difference between responses obtained when the policy shock is calculated using the FFR and the 1-Year Treasury Yield show little difference, however accounting for implied rates via the Shadow Rate has considerable impact on the results. With the threshold level set to the median, both regimes responses shift downwards, and with the 70th percentile, this is only seen in high uncertainty responses. Such results do support the finding of shocks in high uncertainty times having a larger contractionary effect due to uncertainty causing an increase in volatility.

@@

```{=latex}
\caption{Financial stress versus no controls \label{fig:finstress}}
\bigskip
\footnotesize
\textit{Notes}: In both the No Controls and the Fin. Stress estimations, the Shadow Rate is used to estimate policy shocks.
\end{figure}
```
